---
title: "Sample QC analysis"
author: "Johan"
output:
  html_document
  pdf_document
  
params:
  RfunctionsDirectory: "/glob/johanr/scripts/RNAmappingPipeline/R"
  workingDirectory: "."
  resultsDir: "RSeQC"
  metaDataTableTxt: "metaData.table.txt"
  sampleNameColumn: "sampleName" 
  metaDataTableRmd : 'metadata.table.Rmd'

---


This relies on the data output that is being produced from RSeQC and ends up in one folder. All variables that this document is dependent on can be changed  either in the header of by calling the document including parameters. 


#Sample included in the results


```{r, echo=FALSE}

```{r child = paste(params$workingDirectory, params$metaDataTableRmd, sep = "/")}
```


# Distribution of reads that over the different samples.


```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
plot = getTPKMPlots(resultsDir,metaData)
plot
```

#TIN values for the different samples

```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
plot =getTINPlots(resultsDir,metaData)

plot


print ("")
```


#Gene body coverage for the different samples

```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
plot =getGeneBodyCoveragePlots(resultsDir,metaData)


plot[[1]]

plot[[2]]
```


# Fraction of known junctions of all bases on reads used 


```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
plot =getJunctionSaturationPlots(resultsDir,metaData)


plot[[1]]

plot[[2]]
```


# Clipping profile to identify where the soft clipping occurs.
```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
plot =getClippingProfilePlots(resultsDir,metaData)


plot[[1]]

plot[[2]]
```

# Inner distance plot

```{r, echo=FALSE}
RfunctionsDirectory = params$RfunctionsDirectory
RseqFunctionsFile = paste(RfunctionsDirectory,"RSeQCfunctions.R", sep="/")
source(RseqFunctionsFile)
workingDirectory = params$workingDirectory
resultsDir = params$resultsDir
metaDataTableFile = params$metaDataTableTxt

metaData = read.table(paste(workingDirectory,metaDataTableFile,sep= "/"), sep = "\t", header = TRUE,comment.char="");
if(any(colnames(metaData) == "Type")){
  if(any(metaData$Type=="PE")){
    plot =getClippingProfilePlots(resultsDir,metaData)


    plot[[1]]

    plot[[2]]
  }
}else{
  print("No info about paired end reads")
}

```


